\chapter{Acknowledgements}

We would like to express our sincere gratitude to all those who contributed to the successful completion of this project.

First and foremost, we extend our heartfelt thanks to our project guide, \textbf{Saina Deepthi (Lecturer)}, Department of Electrical and Computer Engineering, for her invaluable guidance, continuous support, and encouragement throughout this project. Her expertise in digital electronics and constructive feedback helped us overcome various challenges and achieve our objectives.

We are deeply grateful to the \textbf{Head of Department, Electrical and Computer Engineering}, College of Engineering, Trivandrum, for providing us with the necessary facilities and infrastructure to carry out this project work.

We would like to thank the faculty members of the Department of Electrical and Computer Engineering for their support and for sharing their knowledge, which significantly contributed to our understanding of digital logic design and implementation.

Our sincere appreciation goes to the \textbf{laboratory staff} who assisted us during the hardware implementation phase and ensured the availability of required components and equipment.

We are thankful to \textbf{College of Engineering, Trivandrum} for providing us with an excellent academic environment and resources that facilitated our learning and project development.

We acknowledge our classmates and friends for their constant encouragement and support throughout the duration of this project.

Last but not least, we express our profound gratitude to our \textbf{families} for their unwavering support, patience, and encouragement throughout our academic journey.

\vspace{2em}

\begin{flushright}
\textbf{Group 5 Team Members:} \\
GOWRIKRISHNA V (29) \\
GOWTHAM KRISHNA P K (30) \\
HARIKRISHNAN SANTHOSH (31) \\
HARIKRISHNA S (32) \\
SUDHEESH P (64)
\end{flushright}